---
title: "PBPK Model of PFAS Chemicals in Blood Serum - Child fed formua made with tap water"
author: "Insert Name of Author"
date: "`r format(Sys.time(), '%F')`"
knit: (function(inputFile, encoding) {outdir = file.path(dirname(inputFile), 'markdown', paste0(format(Sys.time(), '%F'))); if(!dir.exists(outdir)){dir.create(outdir, recursive = TRUE)}; rmarkdown::render(inputFile, encoding = encoding, output_format = 'all', output_dir = outdir) })
output:
  word_document: default
  html_document:
    code_folding: hide
    df_print: kable
    toc: yes
    toc_depth: 5
---

The purpose of this model is to calculate the amount of PFAS, PFOA, PFHxS or PFNA (ug/L) in an individual's blood serum, given characteristics of the individual, their tap water concentration & consumption. It performs a Monte Carlo simulation to introduce variation into 14 different variables that define an individual for simulation. This specific example shows PFOA estimation for a child fed formula made with contaminated tap water. 

### Set-up

First, set 'save_output'. If this is set to 'TRUE', simulation results will be saved out to an .Rdata file, otherwise, only test plots will be created in the 'plots' folder

```{r toggle-save-output}
save_output <- FALSE
```

Checks that packages are installed, and install and load them if not. 

```{r libraries}
packages = c("here", # file location referencing
             "readxl", # read excel files
             "dplyr", # data manipulation
             "purrr", # pmap function
             "ggplot2", # plotting
             "matrixStats", # row quantiles
             "lubridate", # extract year from date
             "tictoc") # execution time

package.check <- lapply(
  packages,
  FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE, repos='http://cran.us.r-project.org')
      library(x, character.only = TRUE)
    }
  }
)
```

### User Set Parameters

This section allows users to change settings of the model to produce a simulation for a single individual. The following table defines the parameters

Variable | Description          | Notes
---------|-------------|-------------------------|
chemical | PFAS contaminant |  "PFOA", "PFOS", "PFNA", or "PFHxS"
water_concs | list of drinking water concentrations (ug/L) | concentrations default to 0 before 1960
water_concs_dates | list of dates to apply changes to water concentration | list should be initialized at birth or earlier and dates must be in the format "YYYY-MM-DD"  
perc_tap | list of percentages of daily water intake that comes from tap water | list must contain fractions e.g. 90% = .9
perc_tap_dates | list of dates to apply changes to perc_tap | list should be initialized at birth or earlier and dates must be in the format "YYYY-MM-DD"  
gender | sex | "Female" or "Male"
BW | body weight (kg) | used to select body weight percentiles; the weight should correspond to the age calcuated using the simulation creation date (creation_date), NOT at the end date (ed)
fed_most | whether the individual as an infant was mostly breast fed, fed formula made with tap water, or was fed other store bought formula | "breast milk", "tap water", or "other formula";  "tap water" should be used for adults
fed_mo | number of months after birth the individual was mostly fed fed_most | NA when fed_most = "tap water" or to use defaults of 6 months for fed_most = "breast milk" and 12 months for fed_most = "other formula"; the model data only allows for up to 6 months for breast feeding
mom_pct_tap | the individual's mother's percent of drinking water intake from tap water during pregnancy and breastfeeding | used in placental transfer calculation; must be a fraction and the model defaults to 1 (100%)
numChild | number of children the individual has given birth to | only breast fed children are relevant to a mother's serum calculation
child_gender | list of each child's gender | list must be of length numChild
child_bday | list of each child's birthday | list must be of length numChild and dates must be in the format "YYYY-MM-DD" 
child_bf_mo | list of each child's duration of breast feeding in months| list must be of length numChild; the model data only allows for up to 6 months for breast feeding; if a child was not breast fed use 0 or NA to ignore them
creation_date | manual override for matching calculations run on previous days | defaults to today's date but should correspond with the date the body weight data was provided
niter | number of Monte Carlo iterations | suggested value of 1000; values over 1000 not recommended to avoid intensive computing.  
timestep | number of days between calculations | suggested value of 30
sd | simulation start date | the individual's birthday in the format "YYYY-MM-DD"
ed | simulation end date | may not be exact due to time step

```{r set-param}
# the user sets 
param_list <- list(chemical = "PFOA",
                   water_concs = c(.25,.02), # ug/L
                   water_concs_dates = c("1990-1-1", "2020-1-1"), 
                   perc_tap = c(.9,.25),# percentage  
                   perc_tap_dates = c("1900-1-1", "2021-1-1"), 
                   mom_pct_tap = 1, # percentage
                   gender = "Male", 
                   BW = 20, # kg
                   
                   # If you are a child: (ignored if over 6 years old)
                   fed_most = "tap water", 
                   fed_mo = NA, 
                   
                   # If you are a mother: (ignored if gender = Male or numChild = 0)
                   numChild = 0, 
                   child_gender = c(NA), 
                   child_bday = c(NA), # children's birthdays
                   child_bf_mo = c(NA), # number of months child was breastfed. 
                   
                   creation_date = as.Date("2022-12-31"),  # date output created or body weight provided
                   # we set a creation_date for reproducibility
                   # it also locks the weight provided to a male aged 5
                   niter = 1000, 
                   timestep = 30, # days 
                   sd = as.Date("2017-8-1"), 
                   ed = as.Date("2022-12-31"))
```

### Underlying data 

This section of code loads all the tabs of the source file and uses user set parameters to lookup values. The following table describes the variables that were looked up

Variable | Description 
---------|-----------------------
HL | Half-Life (years), used to calculate DecayPerStep  
V_d | Volume of Distribution (1/kg), used to simulate chemicals in drinking water being distributed throughout the body
MatRemove | Maternal Removal Rate, used to calculate CRBFPerStep (Mother's Clearance Rate from Breast Feeding)
MatXfer | Maternal Transfer Rate, used to calculate BMC (Breast Milk Concenration)
MilkClear | Milk Clearance Rate, used to calculate BMCRPerStep (Breast Milk Clearance Rate)
PlacXfer | Placental Transfer, used to calculate infant starting serum. 
BkgdF, BkgdM | Adult Background Serum, female and male respectively
BkgdFk, BkgdMk | Child Background Serum, female and male respectively; Children are considered under 12 years old

```{r load-data, message=FALSE}
sourceData<-list()
sheetnames<-excel_sheets(path=here("data", "source_PBPK.xlsx"))

for (i in sheetnames){
  data <- read_excel(here("data", "source_PBPK.xlsx"), sheet = i) 
  sourceData[[i]]<-data
  data <- NULL
}
```

### Monte Carlo Variables

This section of code creates a data frame of Monte Carlo variables that will be mapped as inputs into the master function. The following table describes their distribution assumptions

Variable | Distribution | Mean | Standard Deviation | Description
-----|-----|----|-----|-----------------
DWIaf | Normal | 1 | 0.15 | Adjustment factor to Drinking Water Intake
BW | Normal | user entered | 15% of the mean | Individual's current body weight (kg)
HL | Lognormal | source file | source file | look up based on chemical
V_d | Lognormal | source file | source file | look up based on chemical
MatXfer | Normal | source file | 2% of the mean | look up based on chemical
MatRemove | Normal | source file | 2% of the mean | look up based on chemical
MilkClear | Normal | source file | 0.01 | look up based on chemical
PlacXfer | Normal |  source file | 2% of the mean | look up based on chemical
BkgdF | Lognormal |  source file | source file | look up based on chemical
BkgdM | Lognormal |  source file | source file |  look up based on chemical
BkgdFk | Lognormal |  source file | source file |  look up based on chemical
BkgdMk | Lognormal |  source file | source file |  look up based on chemical
concs | Normal | user entered | 15% of the means | Nested data frame for each change in water concentration
perc_tap | Normal | user entered | 15% of the means | Nested data frame for each change in the percent of drinking water intake from tap water

```{r MC}
source(here("scripts","functions","distributions", "monte_carlo_vars.r"))
source(here("scripts","functions","distributions", "icdf_distributions.r"))
source(here("scripts","functions","distributions", "random_distributions.r"))
source(here("scripts","functions","distributions", "shuffle_array.r"))
source(here("scripts","functions","distributions", "make_rnd_stream.r"))

# Creates random variable streams from R model parameters, formatted to enter the main_func
MC_vars <- monte_carlo_vars( param_list = param_list, sourceData = sourceData )
```

### Master Function

The master function constructs a data frame for a single iteration of MC variables, populates it and performs the serum calculations. The output of a single iteration is a list including the entire data frame as a result and a restatement of the parameters

The following table defines the columns of the result data frame:

 Column | Description | Formula
-------|------------|---------------------------------------------
 Time | Exact model age (years)| Days/days_per_year
 Years| Years old| floor(Days/days_per_year)
 Months | Months old | floor(Days/days_per_month)
 Days | Days old| seq(1,total_steps,timestep), where total_steps = ceiling((ed-sd)/timestep)
 Date | Calendar date| seq(sd,ed,timestep)
 DWC | Drinking Water Concentration| MC varied concs looked up with water_concs_dates and set to 0 before 1960
 DWI | Drinking Water Intake| Mean DWI (looked up from source file) * MC varied DWI adjustment factor (DWIaf)
 BW | Body Weight | MC varied BW and the creation_date are used to select the individual's weight percentile at the current age. BW over time is looked up by age from that percentile
 Daily_Dose_DW | Daily Dose from Drinking Water| MC varied perc_tap looked up by date * (DWC/1000)*(DWI/1000)/BW. Set to 0 during breastfeeding and drinking store bought formula
 Vd | Volume of distribution, for each time t | Age_adjust * MC varied V_d. Age_adjust is an adjustment factor for the volume of distribution in children, otherwise it is 1
 Bkgd_serum | Background Serum | MC Varied BkgdF, BkgdM, BkgdFk, or BkgdMk when Days = 1, and a Time Step Adjustment (TSA) for Days > 1 to account for decay.
 Daily_Dose_BM | Daily Dose of Breast Milk. Only used for breastfeeding infants during breastfeeding |  (BMC)*(BMI/1000)/BW_i, where BMC is Breast Milk Concentration, calculated using mother's steady state serum concentration and MC varied MatXfer; BMI is Mean Breast Milk Intake for the infant, looked up from the source file; and BW_i is the Median Body Weight of infants looked up from the source file which differs by gender.
 Serum_b | Serum concentration before elimination | Bkgd_serum + TSA + timestep * (Daily_Dose_DW/Vd), for t = 1. For all t > 1, Serum_a[@t-1] + TSA + timestep * (Daily_Dose_DW/Vd). For infants this is initialized with the steady state value for mother's serum at the time of birth, using MC varied PlacXfer. The Serum_b calculation for infants includes an additional Daily_Dose_BM component. For adults, it is initialized with the background serum.
 Serum_a | Serum concentration after elimination | Serum_b * DecayPerStep. While women are breastfeeding, we substitute CRBFPerStep for DecayPerStep to add additional decay for breast milk clearance. These are calculated with MC varied Halflife, MC varied MilkClearnance and MC varied MatRemove
 id | Unique row identifier | 1:n

### Run Model

```{r run, results='hide'}
source(here("scripts","functions","populate_frame","create_frame.r")) 
# creates initial dataframe with time/age variables
source(here("scripts","functions","populate_frame", "pop_DWI_BMI.r")) 
# populates drinking water intake and breast milk intake
source(here("scripts","functions","populate_frame", "pop_BW.r")) 
# populates body weight
source(here("scripts","functions","populate_frame", "pop_DWC.r")) 
# populates drinking water concs
source(here("scripts","functions","populate_frame", "pop_AA_VD.r")) 
# populates Volume of distribution with  age adjustment factor 
source(here("scripts","functions","populate_frame", "pop_BG.r")) 
# populates background serum

source(here("scripts", "functions", "populate_frame", "age_adjust.r")) 
# helper function for looking up age adjustment factor

source(here("scripts","functions", "serum_calculations","serum_calc.r")) 
# wrapper function for other serum calc functions
source(here("scripts","functions", "serum_calculations","bf_days.r")) 
# which days is there breastfeeding?
source(here("scripts","functions", "serum_calculations","daily_dose_BM.r")) 
# how much PFAS is transferred each timestep through breast milk?
source(here("scripts","functions", "serum_calculations","recursive_serum.r")) 
# recursive formula for calculating serum

source(here("scripts","functions", "main_function.r"))
# serum simulation wrapper function
tic()
results <- pmap(MC_vars, main_func, parameter_list =  param_list, 
                source_data =  sourceData, full = TRUE ) 
# without the argument full = TRUE, only the last timestep will be returned. This is used in keeping object sizes small in model validation when running many individuals. To plot over over time, we must have all timesteps.
toc()
```

This plot is saved to folder

```{r sum-plot}
print(here("plots","PBPK", Sys.Date()))
if(!dir.exists(here("plots", "PBPK", Sys.Date()))){
  dir.create(here("plots","PBPK", Sys.Date()), recursive = TRUE)
}

res_df <- NULL

for (i in 1:param_list$niter){
  cols <- colnames(res_df)
  res_df <- cbind(res_df, results[[i]]$Serum_a)
  colnames(res_df) <- c(cols, paste0("iter",i))
}

res_sum <- rowQuantiles(res_df , probs = c(0.05, 0.95)) %>% as.data.frame()

res_sum$Median <- rowMedians(res_df)
res_sum$Date <- results[[1]]$Date %>% as.Date(origin = "1970-1-1")
colnames(res_sum) <- c("lbound", "ubound", "Mean", "Date")

title <- paste("Blood Serum Concentration of", param_list$chemical)
time_plot <- ggplot(res_sum, aes(x = Date)) + geom_line(aes(y=Mean )) +
  geom_line(aes(y=ubound), linetype = "dashed") + 
  geom_line(aes(y=lbound), linetype = "dashed") +
  labs(x="Year", y="Blood Serum Concentration (ug/L)", title = title) 
time_plot

ggsave(here("plots","PBPK", Sys.Date(),paste0(param_list$chemical,"_",
                                              format(Sys.time(), "%H-%M"),".png")), time_plot)
```

### Save simulation results

The following code can be used to save output and load it back in. Only run if 'save_output' is set to TRUE. 

```{r save-rdata-out }
if(save_output) {

  if(!dir.exists(here("output", "PBPK", Sys.Date()))){
    dir.create(here("output","PBPK", Sys.Date()), recursive = TRUE)
  }

save(results, file = here("output", "PBPK", Sys.Date(), "PBPK_child_tap.Rdata"))

load(file = here("output", "PBPK", Sys.Date(), "PBPK_child_tap.Rdata"))
PBPK_Results <- results; rm(results) }
```

### Session Info

For reproducibility, output the session info. Will provide system information, as well as information about package versions and R versions.

```{r session-info}
print(devtools::session_info())
```
