---
title: "PBPK Model of PFAS Chemicals in Blood Serum - 8 year old Male"
author: "Insert Name of Author"
date: "`r format(Sys.time(), '%F')`"
knit: (function(inputFile, encoding) {outdir = file.path(dirname(inputFile), 'markdown', paste0(format(Sys.time(), '%F'))); if(!dir.exists(outdir)){dir.create(outdir, recursive = TRUE)}; rmarkdown::render(inputFile, encoding = encoding, output_format = 'all', output_dir = outdir) })
output:
  word_document: default
  html_document:
    code_folding: hide
    df_print: kable
    toc: yes
    toc_depth: 5
---

The purpose of this model is to calculate the amount of PFAS, PFOA, PFHxS or PFNA (ug/L) in an individual's blood serum, given characteristics of the individual, their tap water concentration & consumption. It performs a Monte Carlo simulation to introduce variation into 14 different variables that define an individual for simulation. This markdown file creates a figure of serum concentration sensitivities for a 8 year old male.

### Set-up

Define the plot title (plot_title) and the output file name (out_name). Based on the individual, set drop_vars to the variables that do not have any impact and therefore should not be plotted. Set the variable order (vars_order) for faceting subplots together. 

```{r plot-settings}
plot_title <- "8 year old male"
out_name <- "8yo_Male"

drop_vars <-  c( "conc_t1", "MatRemove", "MilkClearance", "PlacXfer", "MatXfer")
vars_order = c("V[d] (L/kg)", "T[1/2] (years)", "C[bgd] (μg/L)", 
                        "DWI (μg/L)", "BW (kg)", "Percent Tap (%)", "DWC (μg/L)")
```

Checks that packages are installed, and install and load them if not.  

```{r libraries}
packages = c("here", # file referencing
             "readxl", # reading excel files
             "dplyr", # data manipulation
             "purrr", # function mapping (pmap)
             "ggplot2", # plotting
             "matrixStats", # quantiles
             "tictoc", # execution time
             "lubridate", # used in mother's pathway
             "grid", # faceting plots together
             "gridExtra")  # facetting plots together 

package.check <- lapply(
  packages,
  FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE, repos='http://cran.us.r-project.org')
      library(x, character.only = TRUE)
    }
  }
)
rm(packages, package.check)
```

### Underlying data 

This section of code loads all the tabs of the source file and will lookup values based on user set parameters. The following table describes the variables that are looked up

Variable | Description 
---------|-----------------------
HL | Half-Life (years), used to calculate DecayPerStep  
V_d | Volume of Distribution (1/kg), used to simulate chemicals in drinking water being distributed throughout the body
MatRemove | Maternal Removal Rate, used to calculate CRBFPerStep (Mother's Clearance Rate from Breast Feeding)
MatXfer | Maternal Transfer Rate, used to calculate BMC (Breast Milk Concenration)
MilkClear | Milk Clearance Rate, used to calculate BMCRPerStep (Breast Milk Clearance Rate)
PlacXfer | Placental Transfer, used to calculate infant starting serum. 
BG_F, BG_M | Adult Background Serum, female and male respectively
BG_Fk, BG_Mk | Child Background Serum, female and male respectively

```{r load-data, message=FALSE}
sourceData<-list()
sheetnames<-excel_sheets(path=here("data", "source_PBPK.xlsx"))

for (i in sheetnames){
  data <- read_excel(here("data", "source_PBPK.xlsx"), sheet = i) 
  sourceData[[i]]<-data
  data <- NULL
}

rm(sheetnames, i, data)
```

### Monte Carlo Variables

This section of code loads functions that create a dataframe of Monte Carlo variables that will be mapped as inputs into the master function. The following table describes their distribution assumptions

Variable | Distribution | Mean | Standard Deviation | Description
-----|-----|----|-----|-----------------
DWIaf | Normal | 1 | 0.15 | Adjustment factor to DWI 
BW | Normal | user entered | 15% of the mean | Individual's current body weight (kg)
HL | Lognormal | source file | source file | lookup based on chemical
V_d | Lognormal | source file | source file | lookup based on chemical
MatXfer | Normal | source file | 2% of the mean | lookup based on chemical
MatRemove | Normal | source file | 2% of the mean | lookup based on chemical
MilkClear | Normal | source file | 0.01 | lookup based on chemical
PlacXfer | Normal |  source file | 2% of the mean | lookup based on chemical
BkgdF | Lognormal |  source file | source file | lookup based on chemical
BkgdM | Lognormal |  source file | source file |  lookup based on chemical
BkgdFk | Lognormal |  source file | source file |  lookup based on chemical
BkgdMk | Lognormal |  source file | source file |  lookup based on chemical
concs | Normal | user entered | 15% of the means | Nested dataframe for each change in water concentration
perc_tap | Normal | user entered | 15% of the means | Nested dataframe for each change in the percent of drinking water intake from tap water

```{r MC-load}
source(here("scripts","functions","distributions", "monte_carlo_vars.r"))
source(here("scripts","functions","distributions", "icdf_distributions.r"))
source(here("scripts","functions","distributions", "random_distributions.r"))
source(here("scripts","functions","distributions", "shuffle_array.r"))
source(here("scripts","functions","distributions", "make_rnd_stream.r")) 
```

### Sensitivity 

This section of code loads functions that will run the sensitivity analysis and creates an output folder for plots

```{r sens-load}
# make a list of parameters - defaults set for 40 year old male and PFOA
source(here("scripts", "analysis", "sensitivity", "param_make.r")) 
# varies monte carlo parameters - defaults to PFOA, defines different function for each person 
source(here("scripts", "analysis", "sensitivity", "mc_create_functions.r"))
# plotting function
source(here("scripts", "analysis", "sensitivity", "tornado_plot.r"))
# run sensitivity through main_func
source(here("scripts", "analysis", "sensitivity", "serum_sensitiv_runs.r"))

last_row <-  function (dframe ) {dframe %>% ungroup () %>% slice_tail(n = 1)}

# plots output to this folder
if(!dir.exists(here("plots", "PBPK", Sys.Date(), out_name))){
  dir.create(here("plots","PBPK", Sys.Date(), out_name), recursive = TRUE)
}

```

### Master Function

This section of code loads modeling functions. The master function constructs a dataframe for a single iteration of MC variables, populates it and performs the serum calculations. The output of a single iteration is a list including the entire dataframe as a result and a restatement of the parameters

The following table defines the columns of the result dataframe:

 Column | Description | Formula
-------|------------|---------------------------------------------
 Time | Exact model age (years)| Days/days_per_year
 Years| Years old| floor(Days/days_per_year)
 Months | Months old | floor(Days/days_per_month)
 Days | Days old| seq(1,total_steps,timestep), where total_steps = ceiling((ed-sd)/timestep)
 Date | Calendar date| seq(sd,ed,timestep)
 DWC | Drinking Water Concentration| MC varied concs looked up with water_concs_dates and set to 0 before 1960
 DWI | Drinking Water Intake| Mean DWI (looked up from source file) * MC varied DWI adjustment factor (DWIaf)
 BW | Body Weight | MC varied BW and the creation_date are used to select the individual's weight percentile at the current age. BW over time is looked up by age from that percentile
 Daily_Dose_DW | Daily Dose from Drinking Water| MC varied perc_tap looked up by date * (DWC/1000)*(DWI/1000)/BW. Set to 0 during breastfeeding and drinking store bought formula
 Vd | Volume of distribution, for each time t | Age_adjust * MC varied V_d. Age_adjust is an adjustment factor for the volume of distribution in children, otherwise it is 1
 Bkgd_serum | Background Serum | MC Varied BkgdF, BkgdM, BkgdFk, or BkgdMk when Days = 1, and a Time Step Adjustment (TSA) for Days > 1 to account for decay.
 Daily_Dose_BM | Daily Dose of Breast Milk. Only used for breastfeeding infants during breastfeeding |  (BMC)*(BMI/1000)/BW_i, where BMC is Breast Milk Concentration, calculated using mother's steady state serum concentration and MC varied MatXfer; BMI is Mean Breast Milk Intake for the infant, looked up from the source file; and BW_i is the Median Body Weight of infants looked up from the source file which differs by gender.
 Serum_b | Serum concentration before elimination | Bkgd_serum + TSA + timestep * (Daily_Dose_DW/Vd), for t = 1. For all t > 1, Serum_a[@t-1] + TSA + timestep * (Daily_Dose_DW/Vd). For infants this is initialized with the steady state value for mother's serum at the time of birth, using MC varied PlacXfer. The Serum_b calculation for infants includes an additional Daily_Dose_BM component. For adults, it is initialized with the background serum.
 Serum_a | Serum concentration after elimination | Serum_b * DecayPerStep. While women are breastfeeding, we substitute CRBFPerStep for DecayPerStep to add additional decay for breast milk clearance. These are calculated with MC varied Halflife, MC varied MilkClearnance and MC varied MatRemove
 id | Unique row identifier | 1:n

```{r model-load}
source(here("scripts","functions","populate_frame","create_frame.r")) 
# creates initial dataframe with time/age variables
source(here("scripts","functions","populate_frame", "pop_DWI_BMI.r"))   
# populates drinking water intake and breast milk intake
source(here("scripts","functions","populate_frame", "pop_BW.r")) 
# populates body weight
source(here("scripts","functions","populate_frame", "pop_DWC.r")) 
# populates drinking water concs
source(here("scripts","functions","populate_frame", "pop_AA_VD.r")) 
# populates Volume of distribution with  age adjustment factor 
source(here("scripts","functions","populate_frame", "pop_BG.r")) 
# populates background serum

source(here("scripts", "functions", "populate_frame", "age_adjust.r")) 
# helper function for looking up age adjustment factor

source(here("scripts","functions", "serum_calculations","serum_calc.r")) 
# wrapper function for other serum calc functions
source(here("scripts","functions", "serum_calculations","bf_days.r")) 
# which days is there breastfeeding?
source(here("scripts","functions", "serum_calculations","daily_dose_BM.r")) 
# how much PFAS is transferred each timestep through breast milk?
source(here("scripts","functions", "serum_calculations","recursive_serum.r")) 
# recursive formula for calculating serum

source(here("scripts","functions", "main_function.r"))
# serum simulation wrapper function
```

### Run Model

#### Make Parameters

The other chemicals will use this parameter list and just change the chemical

```{r param}
days_per_year <- 365.2425
days_per_month <- days_per_year/12
  
param_list_PFOA_ucmr5 <-  param_make(chemical = "PFOA", 
                                    water_concs = c(.1, 0.005), # concentrations in tap water (ug/L)
                                    water_concs_dates = c("1960-1-1", "2020-1-1"), 
                                    perc_tap = c(.9), 
                                    gender = "Male", 
                                    BW = 39.96, niter = 1, timestep = 30, 
                                    sd = as.Date("2014-01-1"), # start date of simulation, 
                                                               # simulated individuals birthdate  (YYYY-MM-DD)
                                    ed = as.Date("2022-01-01"))
```

#### Calculating 5th and 95th percentiles

This section of code gives an example for how the 5th and 95th percentile values were calculated. Values are hard-coded in the mc_create functions for PFOA and entered as inputs for other chemicals. 

```{r 5-95, eval=FALSE}
param_list_PFOA_ucmr5$niter = 1000
MC_vars <- monte_carlo_vars( param_list = param_list_PFOA_ucmr5, sourceData = sourceData )
quantile(MC_vars$BkgdF, c(0.05, 0.5, 0.95)) ;
quantile(MC_vars$MatRemove, c(0.05, 0.5, 0.95)) ;
quantile(MC_vars$MilkClearance, c(0.05, 0.5, 0.95));
quantile(MC_vars$PlacXfer, c(0.05, 0.5, 0.95))  
param_list_PFOA_ucmr5$niter = 1
```

#### PFOA 

Create PFOA sensitivity subplot

```{r PFOA}
pfoa <-  mc_create_child(plist = param_list_PFOA_ucmr5, sourceData = sourceData,
                                     infant = FALSE, Sex = param_list_PFOA_ucmr5$gender, 
                                     Bkgd_range = c(0.084, 1.946178197, 4.52),
                                     BW_range = c(25.44, 39.96, 67.56))

results_pfoa <-serum_sensitiv_runs(sensivary= pfoa , 
                                   plist = param_list_PFOA_ucmr5, 
                                   sourceData = sourceData , 
                                   pfas = param_list_PFOA_ucmr5$chemical )

results_pfoa1 <-  results_pfoa %>%  ungroup()%>%
  mutate(iter = as.character(iter), conc_t1 =  signif(conc_t1, 3), 
         conc_t2 = signif(conc_t2, 3) 
         # correct significant digits issue introduced in mc function for concentrations. 
         ) %>%   
  select(-starts_with("date"), -out_BW)

# drop non-applicable Background columns 
if(param_list_PFOA_ucmr5$gender == "Female"){
  if(as.numeric(param_list_PFOA_ucmr5$ed- param_list_PFOA_ucmr5$sd) / days_per_year < 12){
    results_pfoa1 <- results_pfoa1 %>% select(-starts_with("BkgdM"), - BkgdF) %>% rename("Bkgd" = "BkgdFk") 
  }else{
    results_pfoa1 <- results_pfoa1 %>% select(-starts_with("BkgdM"), - BkgdFk) %>% rename("Bkgd" = "BkgdF") 
  }
}else{
  if(as.numeric(param_list_PFOA_ucmr5$ed- param_list_PFOA_ucmr5$sd) / days_per_year < 12){
    results_pfoa1 <- results_pfoa1 %>% select(-starts_with("BkgdF"), - BkgdM) %>% rename("Bkgd" = "BkgdMk")
  }else{
    results_pfoa1 <- results_pfoa1 %>% select(-starts_with("BkgdF"), - BkgdMk) %>% rename("Bkgd" = "BkgdM")
  }
}

results_pfoa <- results_pfoa1 %>% tidyr::pivot_longer(c(BW:DWI), names_to = "var") %>% 
  group_by(  var) %>% 
  mutate(level = case_when(value == min(value) ~ "low", 
                           value == max(value) ~ "high" 
                           , TRUE ~ "mid"),
         level = ordered(level, c("low", "mid", "high")))


# drop columns with no impact 
dframe <- results_pfoa %>% 
  filter(level != "mid" & !(var %in% drop_vars)) 

# plot
g <- ggtornado(data = dframe, baseline = 4.562544,
          var = "var", level = "level", value = "value", result = "pred_serum_ug_L", 
          Bkgd =  1.946178197,
          var_order = vars_order) 

PFOA <- g+ ggtitle( "PFOA") + theme(plot.title = element_text(hjust = 0.5, size = 16))
PFOA
png(filename = here("plots","PBPK", Sys.Date(), out_name,
                    paste0("PFOA_", format(Sys.time(), "%H-%M"),".png")),
        width = 10, height  = 5, units = "in", res = 100)
grid.draw(PFOA)
dev.off()

```

#### PFOS 

Create PFOS sensitivity subplot

```{r PFOS}
rm(results_pfoa, results_pfoa1,  pfoa)
param_list_PFOS_ucmr5 <-   param_list_PFOA_ucmr5
param_list_PFOS_ucmr5$chemical <- "PFOS"

pfos <- mc_create_child( plist = param_list_PFOS_ucmr5, Sex = param_list_PFOS_ucmr5$gender,
                      sourceData = sourceData , pfas = param_list_PFOS_ucmr5$chemical, infant = FALSE,
                      HL_range =  c(2.2, 3.36, 10.6) , 
                      V_d_range =  c(0.23, 0.32, 0.47),
                      Bkgd_range = c(1.4,	4.067707504, 11.77),
                      BW_range = c(25.44, 39.96, 67.56))

results_pfos <-serum_sensitiv_runs(sensivary= pfos , 
                                         plist = param_list_PFOS_ucmr5, 
                                         sourceData = sourceData , 
                                         pfas = param_list_PFOS_ucmr5$chemical )

results_pfos1 <-  results_pfos %>%  ungroup()%>%
  mutate(iter = as.character(iter), conc_t1 =  signif(conc_t1, 3), 
         conc_t2 = signif(conc_t2, 3) ) %>% 
         # correct significant digits issue introduced in mc function for concentrations. 
           
  select(-starts_with("date"), - out_BW)

# drop non-applicable Background columns 
if(param_list_PFOS_ucmr5$gender == "Female"){
  if(as.numeric(param_list_PFOS_ucmr5$ed- param_list_PFOS_ucmr5$sd) / days_per_year < 12){
    results_pfos1 <- results_pfos1 %>% select(-starts_with("BkgdM"), - BkgdF) %>% rename("Bkgd" = "BkgdFk") 
  }else{
    results_pfos1 <- results_pfos1 %>% select(-starts_with("BkgdM"), - BkgdFk) %>% rename("Bkgd" = "BkgdF") 
  }
}else{
  if(as.numeric(param_list_PFOS_ucmr5$ed- param_list_PFOS_ucmr5$sd) / days_per_year < 12){
    results_pfos1 <- results_pfos1 %>% select(-starts_with("BkgdF"), - BkgdM) %>% rename("Bkgd" = "BkgdMk")
  }else{
    results_pfos1 <- results_pfos1 %>% select(-starts_with("BkgdF"), - BkgdMk) %>% rename("Bkgd" = "BkgdM")
  }
}

results_pfos <- results_pfos1 %>% tidyr::pivot_longer(c(BW:DWI), names_to = "var") %>% 
  group_by(  var) %>% 
  mutate(level = case_when(value == min(value) ~ "low", 
                           value == max(value) ~ "high" 
                           , TRUE ~ "mid"),
         level = ordered(level, c("low", "mid", "high")))

dframe <- results_pfos %>% 
  filter(level != "mid" & !(var %in% drop_vars))

# 7.638046 and 7.638045 both appear in baseline runs, so we use 7.63805

g <- ggtornado(data = dframe, baseline = 7.63805,
          var = "var", level = "level", value = "value", result = "pred_serum_ug_L",
          Bkgd = 4.067707504,
          var_order = vars_order)

PFOS <- g+ ggtitle( "PFOS") + theme(plot.title = element_text(hjust = 0.5, size = 16))
PFOS
# outputs can be lower than the Bkgd because we take 80% of NHANES value
png(filename = here("plots","PBPK", Sys.Date(), out_name,
                    paste0("PFOS_", format(Sys.time(), "%H-%M"),".png")),
        width = 10, height  = 5, units = "in", res = 100)
grid.draw(PFOS)
dev.off()

```

#### PFHxS

Create PFHxS sensitivity subplot 

```{r PFHxS}
rm(results_pfos, results_pfos1,  pfos)
param_list_PFHxS_ucmr5 <-   param_list_PFOA_ucmr5
param_list_PFHxS_ucmr5$chemical <- "PFHxS"

pfhxs <- mc_create_child( plist = param_list_PFHxS_ucmr5, Sex = param_list_PFHxS_ucmr5$gender, 
                      sourceData = sourceData , pfas = param_list_PFHxS_ucmr5$chemical,
                      infant = FALSE, 
                      BW_range = c(25.44, 39.96, 67.56),
                      HL_range =  c(2.4, 8.3, 13.5) , 
                      V_d_range =  c(0.15, 0.29, 0.45),
                      Bkgd_range = c(0.26,0.933249175, 3.34))

results_pfhxs <-serum_sensitiv_runs(sensivary= pfhxs , 
                                         plist = param_list_PFHxS_ucmr5, 
                                         sourceData = sourceData , 
                                         pfas = param_list_PFHxS_ucmr5$chemical)

results_pfhxs1 <-  results_pfhxs %>%  ungroup() %>%
  mutate(iter = as.character(iter), conc_t1 =  signif(conc_t1, 3), 
         conc_t2 = signif(conc_t2, 3)  ) %>%  
         # correct significant digits issue introduced in mc function for concentrations. 
  select(-starts_with("date"), - out_BW)

# drop non-applicable Background columns 
if(param_list_PFHxS_ucmr5$gender == "Female"){
  if(as.numeric(param_list_PFHxS_ucmr5$ed- param_list_PFHxS_ucmr5$sd) / days_per_year < 12){
    results_pfhxs1 <- results_pfhxs1 %>% select(-starts_with("BkgdM"), - BkgdF) %>% rename("Bkgd" = "BkgdFk") 
  }else{
    results_pfhxs1 <- results_pfhxs1 %>% select(-starts_with("BkgdM"), - BkgdFk) %>% rename("Bkgd" = "BkgdF") 
  }
}else{
  if(as.numeric(param_list_PFHxS_ucmr5$ed- param_list_PFHxS_ucmr5$sd) / days_per_year < 12){
    results_pfhxs1 <- results_pfhxs1 %>% select(-starts_with("BkgdF"), - BkgdM) %>% rename("Bkgd" = "BkgdMk")
  }else{
    results_pfhxs1 <- results_pfhxs1 %>% select(-starts_with("BkgdF"), - BkgdMk) %>% rename("Bkgd" = "BkgdM")
  }
}  

results_pfhxs <- results_pfhxs1 %>% 
  tidyr::pivot_longer(c(BW:DWI, "Bkgd"), names_to = "var") %>% 
  group_by(  var) %>% 
  mutate(level = case_when(value == min(value) ~ "low", 
                           value == max(value) ~ "high" 
                           , TRUE ~ "mid"),
         level = ordered(level, c("low", "mid", "high")))

dframe <- results_pfhxs %>% 
  filter(level != "mid" & !(var %in% drop_vars)) 

# 10.315422 and 10.315423 both appear in baseline, so we use 10.31542
g <- ggtornado(data = dframe, baseline = 10.31542,
          var = "var", level = "level", value = "value", result = "pred_serum_ug_L" ,
          Bkgd = 0.933249175, var_order = vars_order)

PFHxS <- g+ ggtitle( "PFHxS")+ theme(plot.title = element_text(hjust = 0.5, size = 16))
PFHxS
png(filename = here("plots","PBPK", Sys.Date(), out_name,
                    paste0("PFHxS_", format(Sys.time(), "%H-%M"),".png")),
        width = 10, height  = 5, units = "in", res = 100)
grid.draw(PFHxS)
dev.off()

```

#### PFNA 

Create PFNA sensitivity subplot
Customized tornado plot call with input together = c("PTF", "C[bgd] (μg/L)", "Percent Tap (%)", "BW (kg)", "Milk Clearance"). This input pastes the labels together in one string to avoid over plotting. 

```{r PFNA}
rm(results_pfhxs, results_pfhxs1,  pfhxs)
param_list_PFNA_ucmr5 <-   param_list_PFOA_ucmr5
param_list_PFNA_ucmr5$chemical <- "PFNA"

pfna <- mc_create_child( plist = param_list_PFNA_ucmr5, Sex = param_list_PFNA_ucmr5$gender, 
                      sourceData = sourceData , pfas = param_list_PFNA_ucmr5$chemical, infant = FALSE,
                      HL_range =  c(1.9, 2.35, 9.5) , 
                      V_d_range =  c(0.1, 0.19, 0.3),
                      Bkgd_range = c(0.2369255, 0.829037043, 2.9009291),
                      BW_range = c(25.44, 39.96, 67.56))

results_pfna <-serum_sensitiv_runs(sensivary= pfna , 
                                   plist = param_list_PFNA_ucmr5, 
                                   sourceData = sourceData , 
                                   pfas = param_list_PFNA_ucmr5$chemical )

results_pfna1 <-  results_pfna %>%  ungroup() %>%
  mutate(iter = as.character(iter), conc_t1 =  signif(conc_t1, 3), 
         conc_t2 = signif(conc_t2, 3) 
         # correct significant digits issue introduced in mc function for concentrations. 
         ) %>%   
    select(-starts_with("date"), - out_BW)

# drop non-applicable Background columns 
if(param_list_PFNA_ucmr5$gender == "Female"){
  if(as.numeric(param_list_PFNA_ucmr5$ed- param_list_PFNA_ucmr5$sd) / days_per_year < 12){
    results_pfna1 <- results_pfna1 %>% select(-starts_with("BkgdM"), - BkgdF) %>% rename("Bkgd" = "BkgdFk") 
  }else{
    results_pfna1 <- results_pfna1 %>% select(-starts_with("BkgdM"), - BkgdFk) %>% rename("Bkgd" = "BkgdF") 
  }
}else{
  if(as.numeric(param_list_PFNA_ucmr5$ed- param_list_PFNA_ucmr5$sd) / days_per_year < 12){
    results_pfna1 <- results_pfna1 %>% select(-starts_with("BkgdF"), - BkgdM) %>% rename("Bkgd" = "BkgdMk")
  }else{
    results_pfna1 <- results_pfna1 %>% select(-starts_with("BkgdF"), - BkgdMk) %>% rename("Bkgd" = "BkgdM")
  }
}

results_pfna <- results_pfna1 %>% tidyr::pivot_longer(c(BW:perc_tap1, DWI), names_to = "var") %>% 
  group_by(  var) %>% 
  mutate(level = case_when(value == min(value) ~ "low", 
                           value == max(value) ~ "high" 
                           , TRUE ~ "mid"),
         level = ordered(level, c("low", "mid", "high")))

dframe <- results_pfna %>% 
  filter(level != "mid" & !(var %in% drop_vars))

# 5.418654 & 5.418653 both appear in baseline runs so we use 5.41865
g <- ggtornado(data = dframe, baseline = 5.41865,
          var = "var", level = "level", value = "value", result = "pred_serum_ug_L",
          Bkgd = 0.829037043,
          var_order = vars_order)

PFNA <- g+ ggtitle( "PFNA") + theme(plot.title = element_text(hjust = 0.5, size = 16))
PFNA
png(filename = here("plots","PBPK", Sys.Date(), out_name,
                    paste0("PFNA_", format(Sys.time(), "%H-%M"),".png")),
        width = 10, height  = 5, units = "in", res = 100)
grid.draw(PFNA)
dev.off()

```

Grid facet plots together

```{r grid-facet}
rm(results_pfna, results_pfna1, pfna)

PFOS_1 <- PFOS+ theme(axis.text.y=element_blank(), 
                          axis.ticks.y=element_blank(), 
                          axis.title.y = element_blank())
PFNA_1 <- PFNA + theme(axis.text.y=element_blank(), 
                          axis.ticks.y=element_blank(), 
                          axis.title.y = element_blank())

joined_plot <- grid.arrange(PFOA, PFOS_1, PFHxS, PFNA_1, nrow = 2, 
                    top = textGrob(plot_title, gp=gpar(fontsize=21,font=8)))

png(filename = here("plots","PBPK", Sys.Date(), paste0(out_name,".png")),
        width = 20, height  = 9, units = "in", res = 100)
grid.draw(joined_plot)
dev.off()
```

### Session Info

For reproducibility, output the session info. Will provide system information, as well as information about package versions and R versions. 
```{r session-info}
print(devtools::session_info())
```
